Reproducible Summary Tables with the \pkg{gtsummary} Package

### 2021-06-21 gtsummary_submission.tex
image related updates
overleaf

Along with descriptive summaries, \pkg{gtsummary} summarizes statistical models, survey data, and builds cross tabulations. 
After data are summarized in a table, \pkg{gtsummary} allows users to combine tables, either side-by-side (with \code{tbl\_merge()}) , or on top of each other (with \code{tbl\_stack()}). 
The table merging and stacking abilities allows analysts to easily synthesize and compare output from several tables and share information in a compact format.
All tables in this manuscript were created using \pkg{gtsummary} v1.4.0.

@@

% code for basic tbl_summary()
% \newpage
\begin{example}
trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(by = trt)
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.73]{summary_basic.png}
  \centering
\end{figure}

@@

% \newpage
\begin{example}
trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(
    by = trt,
    type = age ~ "continuous2",
    label = age ~ "Patient Age",
    statistic = list(age ~ c("{N_nonmiss}", "{mean} ({sd})"),
                     c(grade, response) ~ "{n} / {N} ({p}%)"),
    digits = c(grade, response) ~ c(0, 0, 1),
    missing = "no"
  )
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.73]{summary_plus.png}
  \centering
\end{figure}

@@

\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.73]{summary_plus_plus.png}
  \centering
\end{figure}

@@

tbl_svysummary_1 <-
  svy_trial %>%
  tbl_svysummary(by = trt, include = c(trt, age, grade)) %>%
  add_p()
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.73]{svysummary.png}
  \centering
\end{figure}

@@

\newpage
\begin{example}
trial %>%
  tbl_cross(row = stage, col = trt, percent = "cell") %>%
  add_p(source_note = TRUE)
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.73]{cross.png}
  \centering
\end{figure}

@@

\begin{figure}[h!]
  \includegraphics[scale=0.73]{survfit.png}
  \centering
\end{figure}

@@

% \newpage
\begin{example}
trial %>%
  select(marker, response, trt) %>%
  tbl_summary(by = trt, 
              missing = "no",
              statistic = marker ~ "{mean} ({sd})") %>%
  add_difference() %>%
  add_n() %>%
  add_stat_label() %>%
  bold_labels() %>%
  modify_header(list(label ~ "**Variable**", all_stat_cols() ~ "**{level}**")) %>%
  modify_spanning_header(all_stat_cols() ~ "**Randomization Assignment**") %>%
  as_gt() %>%
  gt::tab_header(
    title = gt::md("**Table 1. Treatment Differences**"),
    subtitle = gt::md("_Highly Confidential_")
  ) %>%
  gt::tab_source_note("Data updated June 26, 2015")
\end{example}
\begin{widefigure}[h!]
  \includegraphics[scale=0.73]{custom.png}
  \centering
\end{widefigure}

@@

\begin{figure}[h!]
  \includegraphics[scale=0.73]{regression.png}
  \centering
\end{figure}

@@

\begin{example}
trial %>%
  select(response, age, grade) %>%
  tbl_uvregression(
    y = response, 
    method = glm,
    method.args = list(family = binomial),
    exponentiate = TRUE,
    pvalue_fun = ~style_pvalue(., digits = 2)
  ) %>%
  add_nevent() %>%
  add_global_p()
\end{example}
\newpage
\begin{figure}[h!]
  \includegraphics[scale=0.73]{uvregression.png}
  \centering
\end{figure}

@@

\begin{figure}[h!]
  \includegraphics[scale=0.73]{merge.png}
  \centering
\end{figure}

@@

For example, using the theme for \textit{The Journal of the American Medical Association} (\textit{JAMA}), large p-values are rounded to two decimal places, confidence intervals are shown as \code{"lb to ub"} instead of \code{"lb, ub"}, and the confidence internal is displayed in the same column as the model coefficients.

@@

\begin{figure}[h!]
  \includegraphics[scale=0.73]{jama.png}
  \centering
\end{figure}

>>>>

Along with descriptive summaries, \pkg{gtsummary} summarizes statistical models, survey data, and builds cross tabulations.
After data are summarized in a table, \pkg{gtsummary} allows users to combine tables, either side-by-side (with \code{tbl\_merge()}) , or on top of each other (with \code{tbl\_stack()}).
The table merging and stacking abilities allows analysts to easily synthesize and compare output from several tables and share information in a compact format.
All tables in this manuscript were created using \pkg{gtsummary} v1.4.1.

@@

% code for basic tbl_summary()
% \newpage
\begin{example}
trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(by = trt)
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.49]{summary_basic.png}
  \centering
\end{figure}

@@

% \newpage
\begin{example}
trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(
    by = trt,
    type = age ~ "continuous2",
    label = age ~ "Patient Age",
    statistic = list(age ~ c("{N_nonmiss}", "{mean} ({sd})"),
                     c(grade, response) ~ "{n} / {N} ({p}%)"),
    digits = c(grade, response) ~ c(0, 0, 1),
    missing = "no"
  )
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.49]{summary_plus.png}
  \centering
\end{figure}

@@

\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.49]{summary_plus_plus.png}
  \centering
\end{figure}

@@

tbl_svysummary_1 <-
  svy_trial %>%
  tbl_svysummary(by = trt, include = c(trt, age, grade)) %>%
  add_p()
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.49]{svysummary.png}
  \centering
\end{figure}

@@

\newpage
\begin{example}
trial %>%
  tbl_cross(row = stage, col = trt, percent = "cell") %>%
  add_p(source_note = TRUE)
\end{example}
\begin{figure}[h!]
  \includegraphics[scale=0.49]{cross.png}
  \centering
\end{figure}

@@

\begin{figure}[h!]
  \includegraphics[scale=0.49]{survfit.png}
  \centering
\end{figure}

@@

% \newpage
\begin{example}
trial %>%
  select(marker, response, trt) %>%
  tbl_summary(by = trt,
              missing = "no",
              statistic = marker ~ "{mean} ({sd})") %>%
  add_difference() %>%
  add_n() %>%
  add_stat_label() %>%
  bold_labels() %>%
  modify_header(list(label ~ "**Variable**", all_stat_cols() ~ "**{level}**")) %>%
  modify_spanning_header(all_stat_cols() ~ "**Randomization Assignment**") %>%
  as_gt() %>%
  gt::tab_header(
    title = gt::md("**Table 1. Treatment Differences**"),
    subtitle = gt::md("_Highly Confidential_")
  ) %>%
  gt::tab_source_note("Data updated June 26, 2015")
\end{example}
\begin{widefigure}[h!]
  \includegraphics[scale=0.49]{custom.png}
  \centering
\end{widefigure}

@@

\begin{figure}[h!]
  \includegraphics[scale=0.49]{regression.png}
  \centering
\end{figure}

@@

\begin{example}
trial %>%
  select(response, age, grade) %>%
  tbl_uvregression(
    y = response,
    method = glm,
    method.args = list(family = binomial),
    exponentiate = TRUE,
    pvalue_fun = ~style_pvalue(., digits = 2)
  ) %>%
  add_nevent() %>%
  add_global_p()
\end{example}
\newpage
\begin{figure}[h!]
  \includegraphics[scale=0.49]{uvregression.png}
  \centering
\end{figure}

@@

\begin{figure}[h!]
  \includegraphics[scale=0.49]{merge.png}
  \centering
\end{figure}

@@

For example, using the theme for \textit{The Journal of the American Medical Association} (\textit{JAMA}), large p-values are rounded to two decimal places, confidence intervals are shown as \code{"lb to ub"} instead of \code{"lb, ub"}, and the confidence interval is displayed in the same column as the model coefficients.

@@

\begin{figure}[h!]
  \includegraphics[scale=0.49]{jama.png}
  \centering
\end{figure}
